Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-03-19 data_appendix.Rmd
Commit data inputs and renaming changes

```{r setup, echo = F, message = F}
knitr::opts_chunk$set(results = 'asis', cache = F)
library(tidyverse)
library(summarytools)
st_options(plain.ascii = F,
           style = "rmarkdown",
           footnote = NA,
           subtitle.emphasis = F,
           dfSummary.silent = T,
           dfSummary.valid.col = F,
           tmp.img.dir = "./tmp",
           dfSummary.style = "grid")
# input Stata file
library(foreign)
data_2005 <- read.dta("C:/Users/katya/Documents/MyDocuments/A Smith College Spring Semester/Natural Resource Economics/seminar-paper-katyagi21/Raw data/seminar_paper_data/2005_hhsurvey.dta")

@@

@@

This Data Appendix documents the data used in "Papter Title". It was prepared in a Rmarkdown document that contains both the documentation and the R code used to prepare the data used in the final estimation. It also includes descriptive statistics for both the original data and the final dataset, with a discussion of any issues of note.

@@

@@

- **hh_id:** This variable is the household ID, which is the same for each member of the household. It is made up of letters and numbers. 
- **variable_name2:** Description of second variable.

@@

*Once you've described the variables, enter an R chunk by selecting Code -> Insert Chunk, or Ctrl+Alt+I, give it a name to describe the dataset you are importing. After importing, export a dataframe summary using the command.*

>>>>

```{r setup, echo = F, message = F}
knitr::opts_chunk$set(results = 'asis', cache = F)
library(tidyverse)
library(summarytools)
st_options(plain.ascii = F,
           style = "rmarkdown",
           footnote = NA,
           subtitle.emphasis = F,
           dfSummary.silent = T,
           dfSummary.valid.col = F,
           tmp.img.dir = "./tmp",
           dfSummary.style = "grid")
# input Stata file, add haven package to make stata 16 version readable 
library(foreign)
library(haven)
data_2005 <- read_dta("C:\\Users\\katya\\Documents\\MyDocuments\\A Smith College Spring Semester\\Natural Resource Economics\\seminar-paper-katyagi21\\Raw data\\seminar_paper_data\\2005_hhsurvey.dta")
#install.packages("reshape")
require(reshape)
data_2005 <- rename(data_2005, c(folio = "hh_id"))
data_2005 <- rename(data_2005, c(s3_08 = "assist"))
data_2005 <- rename(data_2005, c(s3_09 = "reason"))
data_2005 <- rename(data_2005, c(nm_y = "members"))
data_2005 <- rename(data_2005, c(s1_02 = "sex"))
data_2005 <- rename(data_2005, c(s1_03 = "age"))
data_2005 <- rename(data_2005, c(s1_05 = "relation"))
data_2005 <- rename(data_2005, c(s3_01 = "literacy"))
data_2005 <- rename(data_2005, c(s3_04 = "register"))
data_2005 <- rename(data_2005, c(s3_05b = "grade"))
data_2005 <- rename(data_2005, c(s3_07 = "repeated"))

@@

```{r weather data set imported, echo = F, message = F}
#Weather data set

weather <- read_csv("C:\\Users\\katya\\Documents\\MyDocuments\\A Smith College Spring Semester\\Natural Resource Economics\\seminar-paper-katyagi21\\Raw data\\recurrencia_inundacion2002_2012bol.csv")

#rename variables
weather <- rename(weather, c(NOM_DEP = "dept"))
weather <- rename(weather, c(A_2005 = "flood"))

library(dplyr)
weather %>% 
  group_by(dept) %>% 
  summarise(flood = sum(flood))

```

@@

This Data Appendix documents the data used in "Paper Title". It was prepared in a Rmarkdown document that contains both the documentation and the R code used to prepare the data used in the final estimation. It also includes descriptive statistics for both the original data and the final dataset, with a discussion of any issues of note.

@@

```{r renaming variables}

```

@@

- **hh_id:** This variable is the household ID, which is the same for each member of the household. It is made up of letters and numbers. 
- **nro1:** Description of second variable.
- **members:** 
- **urb_rur:** 
- **urb_rur:** 
- **urb_rur:**

@@

*Once you've described the variables, enter an R chunk by selecting Code -> Insert Chunk, or Ctrl+Alt+I, give it a name to describe the dataset you are importing. After importing, export a dataframe summary using the command.*
```{r selecting variables}
# select variables 
hh_vars <- c("hh_id", "assist", "reason", "members", "sex", "age", "relation", "literacy", "register", "grade", "repeated", "dept")
hh_2005 <- data_2005[hh_vars]

data_2005 <- rename(data_2005, c(folio = "hh_id"))
data_2005 <- rename(data_2005, c(s3_08 = "assist"))
data_2005 <- rename(data_2005, c(s3_09 = "reason"))
data_2005 <- rename(data_2005, c(nm_y = "members"))
data_2005 <- rename(data_2005, c(s1_02 = "sex"))
data_2005 <- rename(data_2005, c(s1_03 = "age"))
data_2005 <- rename(data_2005, c(s1_05 = "relation"))
data_2005 <- rename(data_2005, c(s3_01 = "literacy"))
data_2005 <- rename(data_2005, c(s3_04 = "register"))
data_2005 <- rename(data_2005, c(s3_05b = "grade"))
data_2005 <- rename(data_2005, c(s3_07 = "repeated"))
data_2005 <- rename(data_2005, c(depto = "dept"))

#select weather variables
weather_vars <- c("dept", "flood")
weather_2005 <- weather[weather_vars]

```

```{r merging datasets}
total_2005 <- merge(hh_2005, weather_2005,by="dept")
```

```{r exporting data table}
export_summary_table(dfSummary(hh_2005))
```
